Verifying Spatial Properties of Array Computations

### 2017-04-17 oopsla17/model.tex
Fix the subset rel of Region and use macro for region

\begin{defn}[Interval scheme]
  An interval scheme is a finite Cartesian product of intervals on \bz{},
  denoted by the set $\textit{Interval}^N$ for a product of $N$ intervals.
\end{defn}

\begin{defn}[Subscript scheme]
  A \emph{subscript scheme} is an index scheme scheme where:
  %
  \begin{equation*}
    \forall i.\ 1 \leq i \leq N \implies
      \pi_i (S) = \{ p \}
      \; \vee \;
      \pi_i (S) = \interv{-\infty}{\infty}{}
    \end{equation*}
%
  That is, the $i^{th}$ component of the set is either a singleton in \bz{} or
  the infinite interval.
\end{defn}
%
\dnote{May want a predicate as well}

\begin{defn}[Region]
  A region is an index scheme and \region{N} is the set of all regions (\ie{},
  $\region{N} \subseteq \mathcal{P}(\bz)^N)$. The set of all regions is  defined
  as the smallest set satisfying the following:
%
  \begin{enumerate}
    \item If $R$ is in $\textit{Interval}^N$, then $R$ is in \region{N}.
    \item If $R$ and $S$ are in \region{N}, then so are $R \cap S$ and
      $R \cup S$.
  \end{enumerate}
\end{defn}
%
\begin{restatable}{prop}{regionLattice}
  \label{prop:regionLattice}
  $(\region{N},\cup,\cap,\subseteq)$ is a bounded distributive lattice with top
  $\top = \bz{}^N$ and bottom $\bot = \emptyset$.
\end{restatable}
%
\begin{proof}
  Straightforward, the join and meet are mapped to $\cup$ and $\cap$, the set is
  inductively designed to be closed under these operations. Union and
  intersection are associative, commutative, and absroptive under closed sets
  and then they are also for \region{N}. This is enough to show that, it is a
  lattice.

>>>>

\begin{defn}[Interval scheme]\label{def:interval-scheme}
  An interval scheme is a finite Cartesian product of intervals on \bz{},
  denoted by the set $\textit{Interval}^N$ for a product of $N$ intervals.
\end{defn}

\begin{defn}[Subscript scheme]
  A \emph{subscript scheme} is an index scheme scheme where:
  %
  \begin{equation*}
    \forall i.\ 1 \leq i \leq N \implies
      \pi_i (S) = \{ p \}
      \; \vee \;
      \pi_i (S) = \interv{-\infty}{\infty}{}
    \end{equation*}
%
  That is, the $i^{th}$ component of the set is either a singleton in \bz{} or
  the infinite interval.
\end{defn}
%
\begin{defn}[Region]
  A region is an index scheme and \region{N} is the set of all regions (\ie{},
  $\region{N} \subseteq \bz^N)$. The set of all regions is  defined
  as the smallest set satisfying the following:
%
  \begin{enumerate}
    \item If $R$ is in $\textit{Interval}^N$, then $R$ is in \region{N}.
    \item If $R$ and $S$ are in \region{N}, then so are $R \cap S$ and
      $R \cup S$.
  \end{enumerate}
\end{defn}
%
\begin{restatable}{prop}{regionLattice}
  \label{prop:regionLattice}
  $(\region{N},\cup,\cap,\subseteq)$ is a bounded distributive lattice with top
  $\top = \bz{}^N$ and bottom $\bot = \emptyset$.
\end{restatable}
%
\begin{proof}
  Straightforward, the join and meet are mapped to $\cup$ and $\cap$, the set is
  inductively designed to be closed under these operations. Union and
  intersection are associative, commutative, and absroptive under closed sets
  and then they are also for \region{N}. This is enough to show that, it is a
  lattice.
